@article{NRZ-Vikra,
    author = {Neha Singh},
    title = {Data Encoding Techniques},
    journal = {Vikram University, Ujjain},
    year = {n.d.}
}

@misc{NRZ-Community, 
    title = {What Is Non-Return-to-Zero (NRZ) and How Does It Work?}, 
    url = {https://community.fs.com/article/what-is-nonreturntozero-nrz-and-how-does-it-work.html}, 
    publisher = {Community.fs}, 
    author = {George}, 
    year = {2024}, 
    month = {Aug.} 
}

@article{NRZ-unit-2,
    author = {Anonymous}, 
    title = {Unit-2 Data Link Layer}, 
    journal = {I.T.S College Mohan Nagar Ghaziabad}, 
    year = {n.d.}
}

@misc{gforg-manch, 
    title = {Manchester Encoding in Computer Network}, 
    url = {https://www.geeksforgeeks.org/manchester-encoding-in-computer-network/}, 
    publisher = {GeeksforGeeks}, 
    author = {Sakshi98}, 
    year = {2024}, 
    month = {Jan.} 
}

@unpublished{cats-lasers,
    title = {Using Lasers to Send Cats: A Custom Networking Implementation}, 
    author = {Chapell Dylan and Hannebert Mastromarino}, 
    year = {2022}, 
    note = {Unpublished paper}
}

@unpublished{CP341-final,
    title = {CP341 Final Paper}, 
    author = {Behenna M and Hunter Moore Triplett}, 
    year = {2022}, 
    note = {Unpublished paper}
}

@misc{gforg-ascii, 
    title = {Program to Convert Given Binary to Its Equivalent ASCII Character String}, 
    url = {https://www.geeksforgeeks.org/program-to-convert-given-binary-to-its-equivalent-ascii-character-string/}, 
    publisher = {GeeksforGeeks}, 
    author = {Bhukya Vasanth Kumar}, 
    year = {2024}, 
    month = {Feb.} 
}

@misc{free-code-camp, 
    title = {What is the Five Layers Model? The Framework of the Internet Explained}, 
    url = {https://www.freecodecamp.org/news/the-five-layers-model-explained/}, 
    publisher = {freeCodeCamp}, 
    author = {Omer Rosenbaum}, 
    year = {2022}, 
    month = {Oct.} 
}

@misc{E-design, 
    title = {What’s the Difference Between NRZ, NRZI, and Manchester Encoding?}, 
    url = {https://www.electronicdesign.com/technologies/communications/article/21802271/electronic-design-whats-the-difference-between-nrz-nrzi-and-manchester-encoding}, 
    publisher = {Electronic Design}, 
    author = {William Wong}, 
    year = {2024}, 
    month = {Jul.} 
}
